Challenges and Solutions of Developing and Implementing a Revolutionary Novel Desktop-as-a-Service

### 2024-04-26 paper.tex
Some improvements

While developing the novel DaaS platform, we faced multiple obstacles and challenges. Each of these issues belongs to one of the four categories: compatibility, performance, stability, and usability. This section presents the issues we were confronted with, the possible approaches we analyzed, and the solutions we chose.

@@

Examples worth mentioning in this context are eyeOS and SilveOS. The project eyeOS~\cite{liu2012research,vidyabanu2011implementation} which simulated a desktop environment using HTML, PHP, JavaScript, and MySQL. The project SilveOS~\cite{garmpis2016design} mimics the look and feel of Windows 10 in the browser using the discontinued application framework Microsoft Silverlight. Despite being open source, both solutions have never become widely used since it is impossible to import and use native Windows or Linux applications with such solutions. All required applications have to be developed as web applications. This limitation especially caused most potential users to lose interest in web desktops because many popular native applications can hardly be replaced or re-developed, and many feature-rich and well-established Software-as-a-Service offerings like Microsoft Office 365 and Google Docs already exist.

@@

% !!!!!!
% Vermutlich ist das einfach gar nicht relevant hier... wenn doch, müssen wir es sinnvoll einbauen.
% !!!!!!
% On Linux operating systems, sound and microphone devices are accessed via sound servers like PulseAudio and PipeWire, which interact with the sound interface present in the kernel, e.g., Advanced Linux Sound Architecture (ALSA) or Open Sound System (OSS). ...

@@

Compared to RDP, the protocol VNC offers fewer features in Guacamole since it does not support sound on its own. However, Guacamole supports sound using PulseAudio as a workaround solution. VNC also does not offer file transfer and access to external storage media, but as a workaround solution, Guacamole supports file transfer file transfer over SSH using the protocol SFTP.

@@

From the core infratructure to backend services
and user-facing elements, each component inidvidually
has to achieve certain minimum requirements in its own domain
and in order to contribute to the overall performance goals of the whole system.
Hence, we outline key limiting factors that impede performance,
along with our experiences and tailored solutions
aimed at mitigating these challenges.
From our point of view the three most critial performance aspects
for Daas-Systems are:
\begin{itemize}
	\item Infrastructure and Platform
	\item Network Latency
	\item Internal Processing and Communication
\end{itemize}
As there is no generalized measurment system available,
we ordered them by their magnitude of impact
and based them to the best of our knowledge
on the obtained experiences during our research project.
Since each of them have their own characteristics,
specific behavior and requirements, implying a potential impact
on the overall system performance and resource utilization,
we describe them individually and in more detail
in the following seperate subsections.

>>>>

While developing the novel DaaS platform DESIGN, we faced multiple obstacles and challenges. Each of these issues belongs to one of the four categories: compatibility, performance, stability, and usability. This section presents the issues we were confronted with, the possible approaches we analyzed, and the solutions we chose.

@@

Examples worth mentioning in this context are eyeOS and SilveOS. The project eyeOS~\cite{liu2012research,vidyabanu2011implementation} which simulated a desktop environment using HTML, the scripting language PHP, JavaScript, and the MySQL database management system. The project SilveOS~\cite{garmpis2016design} mimics the look and feel of a Windows desktop in the browser using the discontinued application framework Microsoft Silverlight. Despite being open source, both solutions have never become widely used since it is impossible to import and use native Windows or Linux applications with such solutions. All required applications have to be developed as web applications. This limitation especially caused most potential users to lose interest in web desktops because many popular native applications can hardly be replaced or re-developed, and many feature-rich and well-established Software-as-a-Service (SaaS) offerings like Microsoft Office 365 and Google Docs already exist.

@@

@@

Compared to RDP, the protocol VNC offers fewer features in Guacamole since it does not support sound on its own. However, Guacamole supports sound using PulseAudio\footnote{On Linux operating systems, sound and microphone devices are accessed via sound servers like PulseAudio and PipeWire, which interact with the sound interface present in the kernel, e.g., Advanced Linux Sound Architecture (ALSA) or Open Sound System (OSS)} as a workaround solution. VNC also does not offer file transfer and access to external storage media, but as a workaround solution, Guacamole supports file transfer file transfer via the SSH File Transfer Protocol (SFTP) which is an extension of the Secure Shell protocol (SSH).

@@

From the core infratructure to backend services
and user-facing elements, each component inidvidually
has to achieve certain minimum requirements in its own domain
and in order to contribute to the overall performance goals of the whole system.
Hence, we outline key limiting factors that impede performance,
along with our experiences and tailored solutions
aimed at mitigating these challenges.
From our point of view the three most critial performance aspects
for Daas-Systems are:
\begin{itemize}
	\item Infrastructure and Platform
	\item Network Latency and Bandwidth
	\item Internal Processing and Communication
\end{itemize}
As there is no generalized measurment system available,
we ordered them by their magnitude of impact
and based them to the best of our knowledge
on the obtained experiences during our research project.
Since each of them have their own characteristics,
specific behavior and requirements, implying a potential impact
on the overall system performance and resource utilization,
we describe them individually and in more detail
in the following seperate subsections.
